Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2022-11-30 paper.tex
format change for elsevier

% \documentclass[10pt,journal,compsoc]{IEEEtran}
% \usepackage{subfiles}
% \usepackage{url}
% \usepackage{amsmath}
% \usepackage{xspace}
% \usepackage{multirow}
% \usepackage{amssymb}
% \usepackage{algorithm}
% \usepackage{subfig}
% \usepackage[noend]{algpseudocode}
% \renewcommand{\algorithmicrequire}{\textbf{Input:~}}
% \renewcommand{\algorithmicensure}{\textbf{Output:~}}
% \newcommand\ovr[1]{\overrightarrow{#1}}
% \newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
% \usepackage{booktabs}
% \usepackage{array}
% \usepackage{color}
% \usepackage{listings}
% \usepackage{placeins}
% \usepackage{enumitem}
% \usepackage{balance}
% \usepackage{etoolbox}
% \usepackage{lineno,hyperref}
% \newcommand\acrotwo{
% \multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
% }
% \renewcommand{\toprule}{}
% \newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
% \newcommand\kktodo[1]{\textcolor{red}{#1}}
% \newcommand\fixme[1]{\textcolor{red}{#1}}
% \newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
% \newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
% \newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
% \newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
% \newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}

% \let\oldbibliography\thebibliography
% \renewcommand{\thebibliography}[1]{%
%   \oldbibliography{#1}%
%   \setlength{\itemsep}{0pt}%
% }

% \modulolinenumbers[5]

% \renewcommand{\floatpagefraction}{.98}
% % \journal{Journal of Parallel and Distributed Computing}

% %% `Elsevier LaTeX' style
% \bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%

% \begin{document}

% % \begin{frontmatter}
% % \title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}

% % %% Group authors per affiliation:
% % %% or include affiliations in footnotes:
% % \author[add]{Gökhan Göktürk}
% % % \ead{gokhan.gokturk@sabanciuniv.edu}

% % \author[add]{Kamer Kaya}
% % % \ead{kaya@sabanciuniv.edu}

% % \address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}

% % \IEEEtitleabstractindextext{%
\documentclass[10pt,journal,compsoc]{IEEEtran}
\makeatletter
\long\def\@makecaption#1#2{\ifx\@captype\@IEEEtablestring%
\footnotesize\begin{center}{\normalfont\footnotesize #1}\\
{\normalfont\footnotesize\scshape #2}\end{center}%
\@IEEEtablecaptionsepspace
\else
\@IEEEfigurecaptionsepspace
\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ #2}%
\ifdim \wd\@tempboxa >\hsize%
\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ }%
\parbox[t]{\hsize}{\normalfont\footnotesize \noindent\unhbox\@tempboxa#2}%
\else
\hbox to\hsize{\normalfont\footnotesize\hfil\box\@tempboxa\hfil}\fi\fi}
\makeatother

%\DeclareUnicodeCharacter{2212}{-}
\usepackage[utf8]{inputenc}
\ifCLASSOPTIONcompsoc
  % The IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

@@

\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
pdfsubject={Typesetting},%<!CHANGE!
pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!

@@

\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \graphicspath{{./images/}}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}
\else 
\fi
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage[]{booktabs}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
\newcommand\kktodo[1]{\textcolor{red}{#1}}
\newcommand\ggx[1]{\textcolor{blue}{#1}}
\newcommand\fixme[1]{#1}
% \newcommand\fixme[1]{\textcolor{red}{#1}}
\newcommand\acrotwo{
\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
}
% \setlength{\intextsep}{1pt}%

@@

\begin{document}
\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}

\author{G\"{o}khan~G\"{o}kt\"{u}rk
        and~Kamer~Kaya% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G. G\"{o}kt\"{u}rk and K. Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, Istanbul, Turkey.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
}
%FIXME
\markboth{}%
{G\"{o}kt\"{u}rk \MakeLowercase{\textit{et al.}}: Boosting Parallel Influence-Maximization Kernels for Undirected Networks with Fusing and Vectorization}

\maketitle
\begin{abstract}
%     \fixme{
Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. 
% }
In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not step-by-step simulate the diffusion process, have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate, not to count, the number of influenced vertices throughout a diffusion. We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm. In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
\end{abstract}
% } 
% \begin{keyword}
% Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
% \end{keyword}
% \end{frontmatter}

@@

% \begin{figure}[!ht] 
%     \centering
%   \subfloat[\small{IC}\label{fig:ic}]{%
%        \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
%   \subfloat[\small{WC}\label{fig:wc}]{%
%         \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
%     \\% IMAGES HERE
%   \caption{\small{\protect\subref{fig:ic} 
% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
% \protect\subref{fig:wc}
% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
%   }}
%   %\label{fig_ic_model} 
%   \label{fig:xx} 
% \end{figure}

% \begin{itemize}[leftmargin=*]
% \item The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
% In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.

@@

% \setlength{\columnsep}{1.2pt}%
\begin{wrapfigure}{r}{0.35\linewidth}
    \begin{center}
      \includegraphics[width=1\linewidth]{images/ic.pdf}
    \end{center}
    \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
  \end{wrapfigure}
  The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
  % In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing. 
%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. 
We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/fmops.pdf}
    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $u$ with four registers and 4-bit hash functions. (b) \label{fmmerge} Example of union operation on sketches of vertices $u$ and $v$ with four registers. (c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t. sampled subgraph. 
     }\label{fig:fmops} 
    \end{center}
\end{figure}

@@

Figure~\ref{fig:hyperdiff} shows a toy diffusion process on four vertices and a single sample. The process initializes sketches using respective hashes' number of leading zeros. Then larger numbers are started to be pulled from all recently changed neighbors. The same process is repeated for multiple vertices until the new seed vertex is found. To understand the benefits of estimating (instead of counting), we present Fig.~\ref{fig:infuserdiff} which shows an example in the same settings as Fig.~\ref{fig:hyperdiff}. One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas {\sc InFuseR}, or another counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example). Doing otherwise, i.e., computing the reachability set cardinalities for all the vertices at once for a given sample, may require $\mathcal{O}(n^2)$ memory and union operations with $\mathcal{O}(n)$ complexity. Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
%This is why although the reachability sets in Fig.~\ref{fig:infuserdiff} are shown for all vertices with dense vectors, the ones except that of vertex 1 are greyed out since they are not manipulated.
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.95\linewidth]{images/sketchdiff.pdf}
    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph. (a)\label{hyperinit} Toy sketch initialization. (b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices. (c) \label{hyperdiff2} Second level diffusion following (a); only updated vertices' sketches are pulled. 
     }\label{fig:hyperdiff} 
    \end{center}
\end{figure}
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.85\linewidth]{images/infuserdiff.pdf}
    \caption{{\sc InFuseR} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.  (a) \label{fig:infuserinit} Toy graph InFuseR initialization.  (b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$. (c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
     }\label{fig:infuserdiff} 
    \end{center}
\end{figure}

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
    \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}. %\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var. Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç) 
     }\label{fig:sketch-saturation} 
    \end{center}
\end{figure}

@@

% \bibliographystyle{IEEEtran}
% \bibliographystyle{elsarticle-num}
\bibliographystyle{IEEEtranS}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{refs}
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/gokhan.png}}]{G\"{o}khan~G\"{o}kt\"{u}rk} is a PhD candidate at the Faculty of Engineering and Natural Sciences in Sabancı University. He has received his BS and MS degrees from Sabancı University as well. He is interested in High Performance Computing, Parallel Programming, and Graph Processing.
% \end{IEEEbiography}
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Asst. Professor at Sabancı University. After receiving his PhD from Bilkent University, he worked at CERFACS, France, as a post-graduate researcher in the Parallel Algorithms Project. He then joined the Ohio State University in September 2011 as a postdoctoral researcher, and in December 2013, he became a Research Assistant Professor in the Dept. of Biomedical Informatics.
% His current research interests include Parallel Programming, High-Performance Computing, and Cryptography. 
% \end{IEEEbiography}

>>>>

\documentclass[review]{elsarticle}
\usepackage{etoolbox}
\usepackage{lineno,hyperref}
\let\oldbibliography\thebibliography
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
}

\modulolinenumbers[5]

\renewcommand{\floatpagefraction}{.98}
\journal{Expert Systems With Applications}

% %% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%

@@

% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
% pdfsubject={Typesetting},%<!CHANGE!
% pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
% pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!

@@

% \usepackage[pdftex]{graphicx}
% \graphicspath{{./images/}}
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage[]{booktabs}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
\newcommand\kktodo[1]{\textcolor{red}{#1}}
\newcommand\ggx[1]{\textcolor{blue}{#1}}
\newcommand\fixme[1]{#1}
% \newcommand\fixme[1]{\textcolor{red}{#1}}
\newcommand\acrotwo{
\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
}
% \setlength{\intextsep}{1pt}%

@@

\begin{document}

\begin{frontmatter}
\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}

% % %% Group authors per affiliation:
% % %% or include affiliations in footnotes:
\author[add]{Gökhan Göktürk}
% \ead{gokhan.gokturk@sabanciuniv.edu}

\author[add]{Kamer Kaya}
% \ead{kaya@sabanciuniv.edu}

\address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}

\begin{abstract}
%     \fixme{
Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. 
% }
In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not step-by-step simulate the diffusion process, have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate, not to count, the number of influenced vertices throughout a diffusion. We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm. In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
\end{abstract}
% } 
\begin{keyword}
Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
\end{keyword}
\end{frontmatter}

@@

% \begin{figure}[!ht] 
%     \centering
%   \subfloat[\small{IC}\label{fig:ic}]{%
%        \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
%   \subfloat[\small{WC}\label{fig:wc}]{%
%         \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
%     \\% IMAGES HERE
%   \caption{\small{\protect\subref{fig:ic} 
% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
% \protect\subref{fig:wc}
% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
%   }}
%   %\label{fig_ic_model} 
%   \label{fig:xx} 
% \end{figure}
% \FloatBarrier
% \begin{itemize}[leftmargin=*]
% \item The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
% In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.

@@

% \setlength{\columnsep}{1.2pt}%
% \begin{wrapfigure}{r}{0.35\linewidth}
%     \begin{center}
%       \includegraphics[width=1\linewidth]{images/ic.pdf}
%     \end{center}
%     \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
%   \end{wrapfigure}
The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
  % In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing. 
%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. 
We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.8\linewidth]{images/fmops.pdf}
    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $u$ with four registers and 4-bit hash functions. (b) \label{fmmerge} Example of union operation on sketches of vertices $u$ and $v$ with four registers. (c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t. sampled subgraph. 
     }\label{fig:fmops} 
    \end{center}
\end{figure}

@@

Figure~\ref{fig:hyperdiff} shows a toy diffusion process on four vertices and a single sample. The process initializes sketches using respective hashes' number of leading zeros. Then larger numbers are started to be pulled from all recently changed neighbors. The same process is repeated for multiple vertices until the new seed vertex is found. To understand the benefits of estimating (instead of counting), we present Fig.~\ref{fig:infuserdiff} which shows an example in the same settings as Fig.~\ref{fig:hyperdiff}. One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas {\sc InFuseR}, or another counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example). Doing otherwise, i.e., computing the reachability set cardinalities for all the vertices at once for a given sample, may require $\mathcal{O}(n^2)$ memory and union operations with $\mathcal{O}(n)$ complexity. Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
%This is why although the reachability sets in Fig.~\ref{fig:infuserdiff} are shown for all vertices with dense vectors, the ones except that of vertex 1 are greyed out since they are not manipulated.
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.85\linewidth]{images/sketchdiff.pdf}
    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph. (a)\label{hyperinit} Toy sketch initialization. (b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices. (c) \label{hyperdiff2} Second level diffusion following (a); only updated vertices' sketches are pulled. 
     }\label{fig:hyperdiff} 
    \end{center}
\end{figure}
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.85\linewidth]{images/infuserdiff.pdf}
    \caption{{\sc InFuseR} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.  (a) \label{fig:infuserinit} Toy graph InFuseR initialization.  (b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$. (c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
     }\label{fig:infuserdiff} 
    \end{center}
\end{figure}

@@

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
    \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
     }\label{fig:sketch-saturation} 
    \end{center}
\end{figure}

@@

% \bibliographystyle{IEEEtran}
% \bibliographystyle{elsarticle-num}
% \bibliographystyle{IEEEtranS}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{refs}
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/gokhan.png}}]{G\"{o}khan~G\"{o}kt\"{u}rk} is a PhD candidate at the Faculty of Engineering and Natural Sciences in Sabancı University. He has received his BS and MS degrees from Sabancı University as well. He is interested in High Performance Computing, Parallel Programming, and Graph Processing.
% \end{IEEEbiography}
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Asst. Professor at Sabancı University. After receiving his PhD from Bilkent University, he worked at CERFACS, France, as a post-graduate researcher in the Parallel Algorithms Project. He then joined the Ohio State University in September 2011 as a postdoctoral researcher, and in December 2013, he became a Research Assistant Professor in the Dept. of Biomedical Informatics.
% His current research interests include Parallel Programming, High-Performance Computing, and Cryptography. 
% \end{IEEEbiography}
